GWAS datasets for FDR benchmarking

### 2017-09-13 datasets/GWAS/GWAS.Rmd
add triglyceride gwas

>>>>

### GWAS for Lipid Levels

[This study by Willer et al. (2013, Nature Genetics)](http://www.nature.com/ng/journal/v45/n11/full/ng.2797.html) performed a large
GWAS on 188,577 and measured blood lipid levels (as well as several cardiovascular traits).

Let's download the data from the University of Michigan site. The download page 
has a handy [metadata table](http://csg.sph.umich.edu//abecasis/public/lipids2013/)
that describes the contents of the columns in the results files.

There are several types of results files to download (in terms of which phenotype to analyze):

- LDL Cholesterol
- HDL Cholesterol
- Triglycerides
- Total Cholesterol

As well as two types of analyses:

- Joint analyses of GWAS and Metabochip
- analysis of Metabochip

We would like to look at the joint analysis of GWAS + Metabochip since we'd like 
to look at all available SNPs (not just those that have previously shown a possible
association with CVD). We could choose any or all of the traits, but I'll go ahead
and proceed with Triglycerides since I'm curious about the role of genetic variation 
on Triglyceride levels.

```{bash, GWAS3-download, eval=FALSE}
curl -O "http://csg.sph.umich.edu/abecasis/public/lipids2013/jointGwasMc_TG.txt.gz"
```

Next we uncompress the file.

```{bash, GWAS3-unzip, eval=FALSE}
gunzip jointGwasMc_TG.txt.gz 
```

Next, we'll read in the uncompressed `.txt` file into R and verify that it contains
the necessary inputs to run the FDR benchmark comparisons.

```{r, GWAS3-verify-contents}
# read in data
trig <- fread("jointGwasMc_TG.txt", header=TRUE)
dim(trig)
head(trig)
```

- `P_value`:p-value
- `beta`:effect size
- `SE`:standard error
- additional covariates: 
    - `N`: The number of individuals analyzed for this marker.
    - `Freq.A1.1000G.EUR`: Frequency of allele A1 from 1000G EUR sample.

for 2,439,432 SNPs.

```{r, GWAS3-cleanup}
rm(trig)
```
